\section{Metaheuristics}

In order to refine the results, we used metaprocedures to combine the construction heuristic with local searches.

\subsection{VND - Variable Neighborhood Descent}

The VND procedure is very basic. It takes a solution, and systematically applies local searches using different neighborhood structures. It therefore alleviates the problem of local optima by finding only solutions, that are a local optimum with respect to multiple neighborhoods. Depending on the quality of the neighborhoods, these local optima are more likely to also be a global optimum, since the algorithm doesn't get stuck as easilty as if only one neighborhood would have been used.

In our implementation, we used TODO TODO TODO algo, step function


\subsection{GRASP - Greedy Randomized Adaptive Search Procedure}

This approach deals with the problem of local optima in a different way: Instead of escaping them, it is taken for granted that every local search procedure will eventually get stuck in one. Good solutions can nevertheless be produced if the starting point for the local searches are very different, in order for neighborhood searches to find local optima in different areas of the search space. If this procedure is repeated enough times, one can choose the best local optima, of which it is reasonable to assume that it is a very good solution.

Since our construction heuristic offers a simple opportunity for randomisation, we utilised it instead of restricting the decisions of the greedy algorithm, as it is common to do in general. With this randomisation step\footnote{See section \ref{sec:greedy}}, it is still guaranteed for every returned solution to be of high quality, i.e. it is not necessary allow locally bad solutions and ensure for them to maintain a certain objective value threshold.

As local search procedure, VND was used.


